---
title: "Supplement to Criteria to Reevaluate Cutpt"
author: "Charles Tan"
format: pdf
editor: visual
bibliography: Refs.bib
---

When assessing previously determined cut points using in-study baseline samples or for a new population, it is a good practice not too quick to change when the sample size is small. @TAN2020 provided some distribution-free criteria on when the evidence is sufficient that adjustment is needed. Here, I seek to document the calculations in @TAN2020, and provide the detailed criteria for different sample sizes in a table format to assist the use of the paper in practice.

## Calculations behind Table 1

```{r}
source("Funs.R")
CalcLmt(size=c(50,100,150,200,250,300,400,500), pct=0.95)
CalcLmt(size=c(50,100,150,200,250,300,400,500), pct=0.99)
```

## Data behind Figs 1 & 2

Figs 1 & 2 plot the same calculations on more refined grid: from sample size 20 to 500 for tier 1 cut point, and 100 to 500 for tier 2 cut point.

```{r}
T1crit <- CalcLmt(size=20:500, pct=0.95)
T2crit <- CalcLmt(size=100:500, pct=0.99)
```

Here are the detailed criteria for tier 1 cut point:

```{r}
T1crit
```

Here are the detailed criteria for tier 2 cut point:

```{r}
T2crit
```

## Key Function

The calculations are done by customized function **CalcLmt**

```{r}
CalcLmt
```

## Codes to Produce Figs 1&2

Here are the codes to produce Fig 1:

```{r}
#| fig-width: 10
#| fig-height: 8
plot(T1crit$size, T1crit$size-T1crit$upper, xlim=c(0, 500), ylim=c(0, 35), 
     xlab="Dataset Size", ylab="# Above Cut Point", type="l", col="blue")
lines(T1crit$size, T1crit$size-T1crit$lower, lty=1, col="blue")

lines(T2crit$size, T2crit$size-T2crit$upper, lty=1, col="red")
lines(T2crit$size, T2crit$size-T2crit$lower, lty=1, col="red")  

legend(1, 35, lty=c(1,1), col=c("blue","red"), 
       legend=c("Upper and Lower Bounds for Tier 1 Cut Points", 
                "Upper and Lower Bounds for Tier 2 Cut Points"))
```

Here are the codes to produce Fig 2:

```{r}
#| code-overflow: wrap
#| fig-width: 10
#| fig-height: 8
plot(T1crit$size, T1crit$outupp*100, xlim=c(0, 500), ylim=c(0, 15), 
     xlab="Dataset Size", ylab="% Above Cut Point", type="l", col="blue")
lines(T1crit$size, T1crit$outlow*100, lty=1, col="blue")
abline(h=5, lty=2, col="blue")

lines(T2crit$size, T2crit$outupp*100, lty=1, col="red")
lines(T2crit$size, T2crit$outlow*100, lty=1, col="red")  
abline(h=1, lty=2, col="red")

legend(200, 15, lty=c(1,1), col=c("blue","red"), 
       legend=c("Upper and Lower Bounds for Tier 1 Cut Points", 
                "Upper and Lower Bounds for Tier 2 Cut Points"))
```

## Reference
